The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-15 Writeup/paper_v3.tex
Wider bins text included, dist. from Coil included

\subsection{Finding overdensities}
\label{sub:overdensities}
\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited}
  %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
  \caption{Upper panel: Redshift distribution of flux-limited
    ($m_\text{F814W}\le 23.5$) sample with photometric redshift bins
    that are 0.05 wide. Two analytical functions, $p_1(z)$ and $p_2(z)$, defined in Eqns.~\ref{E:pz1} and~\ref{E:pz2} with best fit
    parameters are plotted over it. 
           Lower panel: Plot of $\delta_{g,\text{1D}} =
           N/N_{\text{mod}}-1$ with each functional form as the model
           for each redshift bin. \arun{Note to self: Give parameter values.}
\rachel{How does this figure look if you show the plot range with the
  histogram going to $z=0$ (still only fitting to $0.3<z<1.25$)?  It
  might be nicer to do that and put a vertical line at $z=0.3$ to
  remind the reader that you only fit above that redshift.}
}
  \label{fig:redshift_fluxlimited}
\end{figure}

@@

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{hist2d_mag_mi}
   \caption{2D histogram of galaxies in apparent magnitude
     ($m_\text{F814W}$) and absolute magnitude ($M_I$) in the redshift range $[0.3, 1.0]$. The blue dotted line with a unit slope is a boundary at $z=1$, fitted by eye.
     The green vertical dotted line represents our luminosity cut. } 
   \label{fig:2Dhist}
\end{figure}

@@

Our first approach is to generate a volume-limited sample that is
complete up to $z=1$, by applying a cut on luminosity such that only
galaxies instrinsically brighter than a certain threshold (determined
in detail below) is considered. This threshold is set on the
$k$-corrected $I$-band absolute magnitudes ($M_I$) from the COSMOS PSF-matched
photometry catalog.   The joint distribution of $m_\text{F814W}$ and
$M_I$ is shown in Fig.~\ref{fig:2Dhist}. 
Since the parent sample contains fainter galaxies and is quite
complete to $m_\text{F814W}=25.2$, we compare the $M_I$ distribution
of the $m_\text{F814W}=23.5$ sample with flux-limited samples that
have fainter flux limits, to see where the $m_\text{F814W}<23.5$
sample that we want to use for our tests is no longer complete.
% \begin{figure}
%  \centering
%  a) \includegraphics[width=\columnwidth]{volume_limiting_pdf}
%  b) \includegraphics[width=\columnwidth]{volume_limiting_cdf}
%  \label{fig:volume_limiting_dist}
%  \caption{ ... }
% \end{figure}
At $M_I\sim-22.0$, the
$m_\text{F814W}<23.5$ sample is beginning to lose galaxies in the
$0.9<z<1.0$ redshift bin due to the flux limit. However, the $0.85<z<1$
redshift bin was found to be only moderately overdense, so we choose
to disregard this region for the rest of the analysis, and instead
restrict to $z<0.85$, which is advantageous because it allows us to
choose a somewhat fainter intrinsic luminosity limit for the
analysis.  We relax our luminosity cut %to $-20.8$
so that the sample is volume-limited \emph{not} until $z=1$ but until $z=0.85$. 
We impose the cut at $M_I=-20.8$, which gives 95.3 per cent completeness in
the $0.8 < z \le 0.85$ bin (see Fig.~\ref{fig:MIhist}). The resulting
sample, which has 11~169 galaxies, will be called sample \s$1$ in the remainder
of this work.

@@

\begin{figure*}
 \centering
 \includegraphics[width=2.4\columnwidth]{SMF}
 \caption{Stellar mass distribution for various flux-limited samples
   are shown in three redshift ranges as separate panels. The redshift
   bins have been chosen to facilitate the comparison with  
          a study of the SMF in \protect\cite{Tomczak_SMF}. At high mass, the
          distributions are the same for various flux limits,
          indicating that the samples are complete in that mass
          range. The curves begin to deviate at low masses due to
          incompleteness coming from the flux limit.  The point at
          which the deviation exceeds our threshold determines where the mass cutoff should be to volume-limit the sample.}
 \label{fig:smf}
\end{figure*}

@@

\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_vollimited}
  \caption{
Upper panel: Redshift distribution of volume-limited ($M_I <  -20.8$)
\s$1$ sample with photometric redshift bins that are 0.05 wide. Two
analytical functions with best fit parameters are plotted over it. 
           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) =
           N/N_{\text{mod}}$ with each functional form as the model
           for each redshift bin. \rachel{I am quite concerned that
             something has gone wrong with this fit (in the sense that
           there may be a bug).  Why is the redshift distribution
           shown in blue forced to zero at $z=0.3$?  It should go to
           zero at $z=0$, not $0.3$.  It is clearly not normalized to the same total number as the redshift histogram, either.  In terms of formatting, please
           implement the same changes that I suggested for the
           flux-limited sample redshift distribution plot.}}
  \label{fig:redshift_vollimited}
\end{figure}

@@

% \rachel{As we discussed, you should get rid of the early parts of this
%   regarding second moments, and replace it with a brief description of
%   what shape estimates we use from GalSim (re-Gaussianization).}
% 
% {\bf Should explain in brief Claire's work.} \\

@@

@@

\subsubsection{RMS ellipticites}
\begin{figure}
 \centering
 \includegraphics[width=1.0\columnwidth]{rms_ellip1_noevolution.eps} \\
 \includegraphics[width=1.0\columnwidth]{rms_ellip1_Bbandevolution.eps} \\
% \includegraphics[width=1.0\columnwidth]{rms_ellip2_noevolution.eps} \\
 \caption{RMS distortions as a function of redshift. The horizontal errorbars indicate
          the width of the redshift bin, while the vertical ones
          are $1\sigma$ errorbars obtained by
          bootstrapping. The colors and shapes of the points indicate their
          environmental classification, as shown in the legend. Points with open centers and thick errorbars correspond to the stellar-mass selected sample \s$3$
          and points with filled centers and thin errorbars correspond to the luminosity-selected samples \s$1$ and \s$2$.          
          \rachel{The title and figure clearly show two samples.  The caption needs to explain which are solid points and which are open. Also, the horizontal axis label should
           be either $z$ or ``Photometric redshift ($z$)'', not ``Photo $z$'' (which is not a phrase we have used throughout the paper).  
           The change in horizontal axis label is needed for the other RMS ellipticity plots and anywhere else that it shows up in the paper.} 
           \arun{Done}        
          }
 \label{fig:rms_ellip}

@@

For the luminosity-selected sample without any evolution (\s1), the
RMS distortions (Eq.~\ref{eq:distortion}) of galaxies in each redshift bin are shown
in Fig.~\ref{fig:rms_ellip}.  (\rachel{The figure seems to show two
  samples, not just \s1.  Update the text to reflect this?}) For this and all similar figures, the
colors of the points were selected to easily differentiate between
galaxies in overdense, neutral, and underdense redshift slices.
As shown, the underdense regions
have  higher values for RMS ellipticities when compared to the
overdense regions. The difference between the underdense and overdense
regions for $z>0.5$ is significantly larger than any redshift
evolution across the $z>0.5$ range.  Our conclusions are very similar
if we use the RMS ellipticity from Eq.~\eqref{eq:ellipticity} instead
of the distortion. (\rachel{Our statements at the low redshift end
  regarding the amount of redshift evolution will depend on whether
  we're using the solid or open points, and the text and caption do
  not say which samples they correspond to, so I was not able to
  address this in the text.  Please do that once it is your turn to edit.})

@@

When the $B$-band luminosity evolution is taken into account in
selecting the sample, a systematic increase in the ellipticity at
lower redshifts can be observed. We plot these along with stellar-mass
selected samples, where a similar trend is found, in
Fig.~\ref{fig:rms_ellip_Bband_mass}.

Finally, we show an analogous plot of RMS ellipticities for all three
volume-limited sample using the moments-based shape estimates in
Fig.~\ref{fig:rms_ellip_momentbased}. The conclusions are quite
similar to those using the shapes from the \sersic profile fits, with
the underdense regions standing out in having larger RMS distortions 
than the other redshift slices, an effect that is substantially larger
than any average redshift evolution of the RMS distortions.

@@

\subsection{Other morphological parameters}

For the other morphological parameters that we described in
Sec.~\ref{sub:axisratio}, the \sersic index and bulge-to-total ratio,
we do not compare the distributions directly.  Doing so is relatively
tricky because both distributions have hard cutoffs that are enforced
in the fitting process (\sersic $n$ in the range $[0.25, 6]$ and
$0.05<B/T<0.95$).  The KS and AD statistical tests are both sensitive
to exactly what happens at these hard boundaries in the distributions.
\arun{AD test is actually not so sensitive to the boundaries.}
So, instead of using the full distributions, we will study the
dependence of these quantities on environment by computing the median
values in different redshift slices.  Median values are preferred
over the full distributions or even the sample means since the medians
are more robust to what happens at the edges of the distributions.

@@

%We chose median over mean since \sersic n greater than 6 are truncated to 6. This affects the mean statistic more than the median.
\begin{figure}
 %\centering
 \includegraphics[width=1.0\columnwidth]{median_sersicn}
 \includegraphics[width=1.0\columnwidth]{median_sersicn2}
 \caption{Median values of the \sersic indices for volume-limited
   samples \s$1$ and \s$3$ are plotted (filled centers and thin
   errorbars) in top and bottom panels, respectively, for each
   redshift bin. 
          Median values for the \s$2$ sample are plotted in both the
          panels (open centers and thick errorbars) in both the
          panels.
\rachel{Now I'm really confused.  The text implies
     that the top and bottom are \s1 and \s2 as open points, with \s3 in both
     panels as solid points.  The caption says something different
     regarding which sample is in both panels and which is open
     vs. closed.  Please clarify and make everything consistent!
     Also, you only need to have a legend on one panel, since the
     legends on both panels are the same.  Same comment applies to
     next figure.}}
 \label{fig:median_sersicn}
\end{figure}

\begin{figure}
 %\centering
 \includegraphics[width=1.0\columnwidth]{median_dvcbtt} \
 \includegraphics[width=1.0\columnwidth]{median_dvcbtt2}
  \caption{\rachel{Same confusion here as in previous figure caption;
      please clarify!} Median values of the bulge-to-total ratios for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
          Median values for the \s$2$ sample are plotted in both the panels (open centers and thick errorbars) in both the panels.
          The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.  \rachel{These look so similar that I am questioning the need to have both.  Perhaps remove one and mention that they are nearly identical in the text.}}
 \label{fig:median_dvcbtt}
\end{figure}

@@

\rachel{Here is one thing that is still missing from the results
  section.  We had discussed a number of times lumping the galaxies
  together into slices with larger $\Delta z$ and showing that the
  trends in the shape distributions disappear or are reduced.  You had
  shown me plots for this at some point, but they don't seem to have
  gone into the paper.  Please include them, because it would be
  useful to be able to give some guidance on how wide the redshift
  slices should be to avoid this issue.}

>>>>

\subsection{Finding overdensities}
\label{sub:overdensities}
\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_fluxlimited_withcoil}
  %\caption{\rachel{You show this figure twice.  Why?  The legend needs to say the name of the distribution, not show the functional form.}}
  \caption{Upper panel: Redshift distribution of flux-limited
    ($m_\text{F814W}\le 23.5$) sample with photometric redshift bins
    that are 0.05 wide. Two analytical functions, $p_1(z)$ and $p_2(z)$, defined in Eqns.~\ref{E:pz1} and~\ref{E:pz2} with best fit
    parameters are plotted over it. 
           Lower panel: Plot of $\delta_{g,\text{1D}} =
           N/N_{\text{mod}}-1$ with each functional form as the model
           for each redshift bin. \arun{Note to self: Give parameter values.}
\rachel{How does this figure look if you show the plot range with the
  histogram going to $z=0$ (still only fitting to $0.3<z<1.25$)?  It
  might be nicer to do that and put a vertical line at $z=0.3$ to
  remind the reader that you only fit above that redshift.}
}
  \label{fig:redshift_fluxlimited}
\end{figure}

@@

\begin{figure}
  \centering
   \includegraphics[width=1.0\columnwidth]{hist2d_mag_mi}
   \caption{2D histogram of galaxies in apparent magnitude
     ($m_\text{F814W}$) and absolute magnitude ($M_I$) in the redshift range $[0.3, 1.0]$. The blue dotted line with a unit slope is a boundary at $z=1$, fitted by eye.
     The green vertical dotted line represents our luminosity cut. } 
   \label{fig:2Dhist}
\end{figure}

@@

Call the flux-limited ($m_\text{F814W} \le 23.5$) sample \s$0$. Our first approach is to generate a volume-limited sample that is
complete up to $z=1$, by applying a cut on luminosity such that only
galaxies instrinsically brighter than a certain threshold (determined
in detail below) is considered. This threshold is set on the
$k$-corrected $I$-band absolute magnitudes ($M_I$) from the COSMOS PSF-matched
photometry catalog.   The joint distribution of $m_\text{F814W}$ and
$M_I$ is shown in Fig.~\ref{fig:2Dhist}. 
Since the parent sample contains fainter galaxies and is quite
complete to $m_\text{F814W}=25.2$, we compare the $M_I$ distribution
of the $m_\text{F814W}=23.5$ sample with flux-limited samples that
have fainter flux limits, to see where the $m_\text{F814W}<23.5$
sample that we want to use for our tests is no longer complete.
% \begin{figure}
%  \centering
%  a) \includegraphics[width=\columnwidth]{volume_limiting_pdf}
%  b) \includegraphics[width=\columnwidth]{volume_limiting_cdf}
%  \label{fig:volume_limiting_dist}
%  \caption{ ... }
% \end{figure}
At $M_I\sim-22.0$, the
$m_\text{F814W}<23.5$ sample is beginning to lose galaxies in the
$0.9<z<1.0$ redshift bin due to the flux limit. However, the $0.85<z<1$
redshift bin was found to be only moderately overdense, so we choose
to disregard this region for the rest of the analysis, and instead
restrict to $z<0.85$, which is advantageous because it allows us to
choose a somewhat fainter intrinsic luminosity limit for the
analysis.  We relax our luminosity cut %to $-20.8$
so that the sample is volume-limited \emph{not} until $z=1$ but until $z=0.85$. 
We impose the cut at $M_I=-20.8$, which gives 95.3 per cent completeness in
the $0.8 < z \le 0.85$ bin (see Fig.~\ref{fig:MIhist}). The resulting
sample, which has 11~169 galaxies, will be called sample \s$1$ in the remainder
of this work.

@@

\begin{figure*}
 \centering
 \includegraphics[width=2.2\columnwidth]{SMF}
 \caption{Stellar mass distribution for various flux-limited samples
   are shown in three redshift ranges as separate panels. The redshift
   bins have been chosen to facilitate the comparison with  
          a study of the SMF in \protect\cite{Tomczak_SMF}. At high mass, the
          distributions are the same for various flux limits,
          indicating that the samples are complete in that mass
          range. The curves begin to deviate at low masses due to
          incompleteness coming from the flux limit.  The point at
          which the deviation exceeds our threshold determines where the mass cutoff should be to volume-limit the sample.}
 \label{fig:smf}
\end{figure*}

@@

\begin{figure}
 \centering
  \includegraphics[width=\columnwidth]{redshift_vollimited_withcoil}
  \caption{
Upper panel: Redshift distribution of volume-limited ($M_I <  -20.8$)
\s$1$ sample with photometric redshift bins that are 0.05 wide. Two
analytical functions with best fit parameters are plotted over it. 
           Lower panel: Plot of $(1+\delta_{g,\text{1D}}) =
           N/N_{\text{mod}}$ with each functional form as the model
           for each redshift bin. \rachel{I am quite concerned that
             something has gone wrong with this fit (in the sense that
           there may be a bug).  Why is the redshift distribution
           shown in blue forced to zero at $z=0.3$?  It should go to
           zero at $z=0$, not $0.3$.  It is clearly not normalized to the same total number as the redshift histogram, either.  In terms of formatting, please
           implement the same changes that I suggested for the
           flux-limited sample redshift distribution plot.}}
  \label{fig:redshift_vollimited}
\end{figure}

@@

% \rachel{As we discussed, you should get rid of the early parts of this
%   regarding second moments, and replace it with a brief description of
%   what shape estimates we use from GalSim (re-Gaussianization).}
% 
% {\bf Should explain in brief Claire's work.} \\
\begin{figure*}
 \centering
 \includegraphics[width=2.2\columnwidth]{sample_histograms}
 \caption{The distributions of the morphological parameters of interest, namely the distortion, \sersic index and \btt are presented. 
          The shape of the distribution depends on the way the volume-limiting process is carried out. \s$0$ refers to the flux-limited ($m_\text{F814}\le23.5$) sample
          and \s$1$, \s$2$ and \s$3$ refer to the volume-limited samples, as discussed in Sec.~\ref{sub:volumelimiting}}
  \label{fig:sample_histograms}
\end{figure*}

@@

\arun{New paragraph:} Fig.~\ref{fig:sample_histograms} show the distribution of these morphological and shape parameters for the flux-limited sample \s$0$ and the various
volume-limited samples - \s$1$, \s$2$ and \s$3$. It is important to understand the biases in selecting the galaxies in each of the volume-limiting process to be able to interpret the results.
For instance, galaxies with lower \sersic indices are preferentially selected in \s$2$ when compared to \s$1$ and \s$3$. And similarly, galaxies with low ellipticity/distortion values
are rejected in generating \s$2$ and \s$3$ while they are retained in \s$1$.

@@

\subsubsection{RMS ellipticites}
\begin{figure}
 \centering
 \includegraphics[width=1.0\columnwidth]{rms_ellip1_noevolution.eps} \\
 \includegraphics[width=1.0\columnwidth]{rms_ellip1_Bbandevolution.eps} \\
% \includegraphics[width=1.0\columnwidth]{rms_ellip2_noevolution.eps} \\
 \caption{RMS ellipticities as a function of redshift. The horizontal errorbars indicate
          the width of the redshift bin, while the vertical ones
          are $1\sigma$ errorbars obtained by
          bootstrapping. The colors and shapes of the points indicate their
          environmental classification, as shown in the legend. Points with open centers and thick errorbars correspond to the stellar-mass selected sample \s$3$
          and points with filled centers and thin errorbars correspond to the luminosity-selected samples \s$1$ and \s$2$.          
          \rachel{The title and figure clearly show two samples.  The caption needs to explain which are solid points and which are open. Also, the horizontal axis label should
           be either $z$ or ``Photometric redshift ($z$)'', not ``Photo $z$'' (which is not a phrase we have used throughout the paper).  
           The change in horizontal axis label is needed for the other RMS ellipticity plots and anywhere else that it shows up in the paper.} 
           \arun{Done}        
          }
 \label{fig:rms_ellip}

@@

For the luminosity-selected samples (\s$1$,\s$2$), the
RMS ellipticities (Eq.~\eqref{eq:ellipticity}) of galaxies in each redshift bin are shown
in Fig.~\ref{fig:rms_ellip}. In each case, the RMS ellipticities from the mass-selected sample (\s$3$) are also plotted.
When the $B$-band luminosity evolution is taken into account in selecting the sample, a systematic increase in the ellipticity at
lower redshifts can be observed (bottom panel).The stellar-mass selected sample exhibits a similar trend.

(\rachel{The figure seems to show two  samples, not just \s1.  Update the text to reflect this?} \arun{Fixed.}) 
For figures upto Fig.~\ref{fig:median_dvcbtt}, the colors of the points were selected to easily differentiate between galaxies in overdense, neutral, and underdense redshift slices.
Points with unfilled centers and thicker errorbars correspond to the \s$3$ sample and points with filled centers and thinner errorbars correspond to the luminosity-selected samples (\s$1$ or \s$2$).

As shown in Fig.~\ref{fig:rms_ellip}, the underdense regions have  higher values for RMS ellipticities when compared to the
overdense regions. The difference between the underdense and overdense
regions for $z>0.5$ is significantly larger than any redshift
evolution across the $z>0.5$ \arun{$z<0.5$, you mean?} range.  
Our conclusions are very similar if we use the RMS distortion from Eq.~\eqref{eq:distortion} instead
of the ellipticities. (\rachel{Our statements at the low redshift end
  regarding the amount of redshift evolution will depend on whether
  we're using the solid or open points, and the text and caption do
  not say which samples they correspond to, so I was not able to
  address this in the text.  Please do that once it is your turn to edit.})

@@

Next, we show an analogous plot of RMS ellipticities \arun{Is this ellipticity or distortion?} for all three
volume-limited sample using the moments-based shape estimates in
Fig.~\ref{fig:rms_ellip_momentbased}. The conclusions are quite
similar to those using the shapes from the \sersic profile fits, with
the underdense regions standing out in having larger RMS distortions 
than the other redshift slices, an effect that is substantially larger
than any average redshift evolution of the RMS distortions.

@@

\subsection{Morphological parameters}

For the morphological parameters that we described in
Sec.~\ref{sub:axisratio}, the \sersic index and bulge-to-total ratio,
we do not compare the distributions directly.  Doing so is relatively
tricky because both distributions have hard cutoffs that are enforced
in the fitting process (\sersic $n$ in the range $[0.25, 6]$ and
$0.05<B/T<0.95$). See Fig.~\ref{fig:sample_histograms}.
The KS and AD statistical tests are both sensitive to exactly what happens at these hard boundaries in the distributions.
\arun{AD test is actually not so sensitive to the boundaries.}
So, instead of using the full distributions, we will study the
dependence of these quantities on environment by computing the median
values in different redshift slices.  Median values are preferred
over the full distributions or even the sample means since the medians
are more robust to what happens at the edges of the distributions.

@@

%We chose median over mean since \sersic n greater than 6 are truncated to 6. This affects the mean statistic more than the median.
\begin{figure}
 %\centering
 \includegraphics[width=1.0\columnwidth]{median_sersicn}
 \includegraphics[width=1.0\columnwidth]{median_sersicn2}
 \caption{Median values of the \sersic indices for volume-limited
   samples \s$1$ and \s$2$ are plotted (filled centers and thin
   errorbars) in top and bottom panels, respectively, for each
   redshift bin. 
          Median values for the \s$3$ sample are plotted in both the
          panels (open centers and thick errorbars) in both the
          panels.
\rachel{Now I'm really confused.  The text implies
     that the top and bottom are \s1 and \s2 as open points, with \s3 in both
     panels as solid points.  The caption says something different
     regarding which sample is in both panels and which is open
     vs. closed.  Please clarify and make everything consistent!
     Also, you only need to have a legend on one panel, since the
     legends on both panels are the same.  Same comment applies to
     next figure.} 
\arun{Sorry, my bad. I have made the convention about the point markers and errorbar thickness in the text and in Fig.~\ref{fig:rms_ellip}}     
     }
 \label{fig:median_sersicn}
\end{figure}

\begin{figure}
 %\centering
 \includegraphics[width=1.0\columnwidth]{median_dvcbtt} \
 \includegraphics[width=1.0\columnwidth]{median_dvcbtt2}
  \caption{\rachel{Same confusion here as in previous figure caption;
      please clarify!} Median values of the bulge-to-total ratios for volume-limited samples \s$1$ and \s$2$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
          Median values for the \s$3$ sample are plotted in both the panels (open centers and thick errorbars) in both the panels.
          The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.  \rachel{These look so similar that I am questioning the need to have both.  Perhaps remove one and mention that they are nearly identical in the text.}}
 \label{fig:median_dvcbtt}
\end{figure}

\subsection{Wider bins}

We now repeat the analysis with wider redshift bins. Pretending to be ignorant of any overdensities and underdensities along the line of sight, we choose the slices in redshift to be $\left[ 0.3 - 0.5 \right]$,
$\left[ 0.5 - 0.7\right]$ and $\left[ 0.7 - 0.85\right]$.
\begin{figure}
 \centering
 \includegraphics[width=1.0\columnwidth]{rms_ellip1_noevolution_wide} \
 \includegraphics[width=1.0\columnwidth]{rms_ellip1_Bbandevolution_wide}
 \caption{ RMS ellipticities as a function of redshift. The horizontal errorbars indicate
           the width of the redshift bin, while the vertical ones are $1\sigma$ errorbars obtained by
           bootstrapping. Points with open centers and thick errorbars correspond to the stellar-mass selected sample \s$3$
           and points with filled centers and thin errorbars correspond to the luminosity-selected samples \s$1$ and \s$2$.    
         }
 \label{fig:rms_ellip_wide}
\end{figure}

\begin{figure}
 \centering
 \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_noevolution_wide} \
 \includegraphics[width=1.0\columnwidth]{rms_ellip_momentbased_Bbandevolution_wide}
 \caption{ RMS distortions as a function of redshift. The horizontal errorbars indicate
           the width of the redshift bin, while the vertical ones are $1\sigma$ errorbars obtained by
           bootstrapping. Points with open centers and thick errorbars correspond to the stellar-mass selected sample \s$3$
           and points with filled centers and thin errorbars correspond to the luminosity-selected samples \s$1$ and \s$2$.    
         }
 \label{fig:rms_ellip_momentbased_wide}         
\end{figure}

\begin{figure}
 \centering
 \includegraphics[width=1.0\columnwidth]{median_dvcbtt_wide} \
 \includegraphics[width=1.0\columnwidth]{median_dvcbtt2_wide} 
 \caption{ Plot of median values of \btt, as a function of redshift. The horizontal errorbars indicate
           the width of the redshift bin, while the vertical ones are $1\sigma$ errorbars obtained by
           bootstrapping. Points with open centers and thick errorbars correspond to the stellar-mass selected sample \s$3$
           and points with filled centers and thin errorbars correspond to the luminosity-selected samples \s$1$ and \s$2$.    
         }
  \label{fig:median_dvcbtt_wide}
\end{figure}

\begin{figure}
 \centering
 \includegraphics[width=1.0\columnwidth]{median_sersicn_wide} \
 \includegraphics[width=1.0\columnwidth]{median_sersicn2_wide} 
 \caption{ Plot of median values of \sersic index, as a function of redshift. The horizontal errorbars indicate
           the width of the redshift bin, while the vertical ones are $1\sigma$ errorbars obtained by
           bootstrapping. Points with open centers and thick errorbars correspond to the stellar-mass selected sample \s$3$
           and points with filled centers and thin errorbars correspond to the luminosity-selected samples \s$1$ and \s$2$.    
         }
 \label{fig:median_sersicn_wide}
\end{figure}

Comparing Figs.~\ref{fig:rms_ellip_wide}, ~\ref{fig:rms_ellip_momentbased_wide}, ~\ref{fig:median_dvcbtt_wide} and ~\ref{fig:median_sersicn_wide} to the corresponding figures from earlier, we observe that the 
range of values they assume have become smaller and so have the vertical errorbars, due to the increase in the number of galaxies in each redshift bin. The results do not suggest that statistic values
are all consistent across all redshift bins. However, it seems to suggest that when we choose wider bins, which include overdense and underdense structures in them and thus average out,
the shape and the morphological parameters are affected lesser by the cosmic variance.

@@

\rachel{Here is one thing that is still missing from the results
  section.  We had discussed a number of times lumping the galaxies
  together into slices with larger $\Delta z$ and showing that the
  trends in the shape distributions disappear or are reduced.  You had
  shown me plots for this at some point, but they don't seem to have
  gone into the paper.  Please include them, because it would be
  useful to be able to give some guidance on how wide the redshift
  slices should be to avoid this issue.}
\arun{Included now as the last part in the section on results. Do you want me to move it down to this section?}
